%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Andrew Amontree}
\address{525 Glen Iris Dr NE \linebreak Unit 2537 \linebreak Atlanta GA 30308}
\contacts{(678) 521-1296 \linebreak aamontree3@gatech.edu}

\begin{document}

	% Print the header
	\makeheader
	
	% Print the content
	\begin{cvsection}{Education}
		\begin{cvsubsection}{Atlanta, GA}{Georgia Institute of Technology}{Aug 2017 -- May 2020}
			\begin{itemize}
				\item MS in Computer Science
				\item Specialization: Machine Learning
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{Atlanta, GA}{Georgia Institute of Technology}{Aug 2012 -- May 2016}
			\begin{itemize}
				\item BS in Computer Science
				\item Threads: People \& Information Internetworks
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item Java, Python, SQL, Swift
				\item Apache Beam, Apache Spark, PyTorch, Spring Boot, TensorFlow, UIKit
				\item Google Cloud Platform (GCP), Git, Xcode, IntelliJ, Pivotal Tracker, Concourse CI/CD, Charles Proxy
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Senior Software Engineer}{The Home Depot}{Jan 2018 -- Present}
			\textit{Recommendations \& Personalization}
			\begin{itemize}
				\item Lead the engineering effort to deliver machine-learning driven visual recommendations on homedepot.com (Apache Beam, Python)
				\item Managed Search team undergraduate intern projects for three consecutive semesters serving as a technical guide and mentor
				\item Co-lead weekly career development learning sessions for 8 summer interns from across the company
			\end{itemize}
			\textit{Cloud Platform Engineering}
			\begin{itemize}
				\item Developed and launched an intelligent reverse proxy / load balancer that routes over one hundred million requests to The Home Depot website every day (Java, GCP, Netty, Undertow).
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Teaching Assistant}{Georgia Institute of Technology}{Aug 2018 -- Jan 2019}
			CS 7646: Machine Learning for Trading
		\end{cvsubsection}
		
		\begin{cvsubsection}{Software Engineer}{POSSIBLE Mobile}{May 2016 -- Jan 2018}	
			\textit{iOS development and consulting for a Fortune 100 multimedia company}
			\begin{itemize}
				\item Worked on the official app of a major professional sports league for iOS, Apple TV, and Roku devices (Brightscript, Objective-C, Swift).
				\item Developed new features, performed code reviews, and worked with client to scope out requirements.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Research Assistant}{Georgia Tech Sonification Lab}{Aug 2014 -- May 2015}		
			\begin{itemize}
				\item Built several mockups of automotive HMIs with novel layouts for navigation and mobile device integration. (C++, QML, Qt).
				\item Collected measures including driving performance, workload, and physiological responses for psychological studies.
				\item Gable., T.M., Walker, B.N., \& Amontree, A.S. (2015). ``Investigating a new display format for CarPlay to decrease impact of mode change inputs" (AutomotiveUI 2015).
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Software Engineer, Intern}{Panasonic Automotive Systems}{Jan 2014 -- May 2014}
			\begin{itemize}
				\item Created a prototype automotive infotainment interface for Apple CarPlay integration on the QNX platform (C++).
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Software Engineer, Intern}{NexTraq}{May 2013 -- Dec 2013}
			\begin{itemize}
				\item Developed new features and engineered solutions to critical bugs in the NexTraq Connect mobile application (Appcelerator Titanium, Javascript).
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Technical Experience}
		\begin{cvsubsection}{Projects}{}{}
			\begin{itemize}
				\item \textbf{Gatekeeper} (2018). Web application that securely manages an apartment gate callbox (Node.js, Twilio, AWS).
				\item \textbf{Global Hepatitis Outbreak and Surveillance Technology (GHOST)} (Spring 2016). Undergraduate Capstone Design Project: An interactive node-link visualization for the Centers for Disease Control (D3.js).
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
\end{document}
